RProtoBuf: Efficient Cross-Language Data Serialization in R

### 2013-12-17 papers/rjournal/eddelbuettel-francois-stokely.tex
minor edits
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@555 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\abstract{Modern data collection and analysis pipelines often involve
 a sophisticated mix of applications written in general purpose and
 specialized programming languages.  Protocol Buffers are a popular
 method of serializing structured data between applications.  The
 \textbf{RProtoBuf} package provides a complete interface to this
 library.
TODO keep it less than 150 words.
}

@@

Comparison with what people start with in R : CSV
comparison with what is only slightly better: JSON

@@

\address{Author One\\
  Affiliation\\
  Address\\
  Country}
\email{author1@work}

>>>>

\abstract{Modern data collection and analysis pipelines often involve
 a sophisticated mix of applications written in general purpose and
 specialized programming languages.  Protocol Buffers are a popular
 method of serializing structured data between applications---while remaining
 indendent of programming languages or operating system.  The
 \textbf{RProtoBuf} package provides a complete interface to this
 library.
 %TODO(ms) keep it less than 150 words.
}

%TODO(de) 'protocol buffers' or 'Protocol Buffers' ?

@@

Comparison with what people start with in R : CSV

Comparison with what is only slightly better: JSON

Maybe mention related, competing approaches such as BSON, Thrift, msgpack,
though we get carried away.

@@

\address{Dirk Eddelbuettel\\
  Debian and R Projects\\
  711 Monroe Avenue, River Forest, IL 60305\\
  USA}
\email{edd@debian.org}
